---
title: Short Paper
author:
  - name: Alice Anonymous
    email: alice@example.com
    affiliation: Some Institute of Technology
    footnote: 1
  - name: Bob Security
    email: bob@example.com
    affiliation: Another University
  - name: Cat Memes
    email: cat@example.com
    affiliation: Another University
    footnote: 2
  - name: Derek Zoolander
    email: derek@example.com
    affiliation: Some Institute of Technology
    footnote: 2
address:
  - code: Some Institute of Technology
    address: Department, Street, City, State, Zip
  - code: Another University
    address: Department, Street, City, State, Zip
footnote:
  - code: 1
    text: "Corresponding Author"
  - code: 2
    text: "Equal contribution"
abstract: |
  # Abstract
  
  Noise, as the term itself suggests, is most often seen a nuisance to ecological insight, a inconvenient reality that must be acknowledged, a haystack that must be stripped away to reveal the processes of interest underneath. Yet despite this well-earned reputation, noise is often interesting in its own right: noise can induce novel phenomena that could not be understood from some underlying determinstic model alone.  Nor is all noise the same, and close examination of differences in frequency, color or magnitude can reveal insights that would otherwise be inaccessible.  Yet with each aspect of stochasticity leading to some new or unexpected behavior, the time is right to move beyond the familiar refrain of "everything is important" [@harrison_back_2019].  Stochastic phenomena can suggest new ways of inferring process from pattern, and thus spark more dialog between theory and empirical perspectives that best advances the field as a whole. I highlight a few compelling examples, while observing that the study of stochastic phenomena are only beginning to make this translation into empirical inference.  There are rich opportunities at this interface in the years ahead.  
  
  This line I wrote from GitHub, yeah yeah, I'm that cool.
  
  \newpage

journal: "An awesome journal"
date: "`r Sys.Date()`"
layout: review
bibliography: My_Ecology_Letters_article.bib  # mybibfile.bib #  #
# linenumbers: true
# numbersections: true
csl: elsevier-harvard.csl
output: rticles::elsevier_article
preamble: |
  \usepackage[nomarkers]{endfloat}
  \linenumbers
  \usepackage{setspace}
  \doublespacing

---

```{r, include=F}
# install.packages("rticles")
# https://github.com/crsh/citr
# https://annakrystalli.me/rrtools-repro-research/paper.html

# To install TinyTeX for R users: to be able to compile a Rmd to PDF
# https://yihui.name/tinytex/#for-r-users
# install.packages('tinytex')
# tinytex::install_tinytex()

# To include citations from a Bib-TeX-file
# install.packages("citr")
library(citr)
```

```{r, include = F}
# BUGs
# for Harrison et al 2019, I had to change the name of the reference from "harrison_back--back_2019" to "harrison_back_2019", reload the content of directory and restart the R session

# Git and Github stuff
# https://happygitwithr.com/push-pull-github.html
```


```{r libraries, include = F}
knitr::opts_chunk$set(echo = FALSE, message=FALSE, warning=FALSE, dev="cairo_pdf", fig.width=7, fig.height=3.5)
library(dplyr)
library(readr)
library(ggplot2)
library(ggthemes)
# library(rrcompendium)

theme_set(theme_grey())

```

```{r, include = F}
add.transparency.colour <- function(colours,alpha=0.35){
  col.rgb <- col2rgb(colours)
  colnames(col.rgb) <- colours
  output <- c()
  for(i in 1:length(col.rgb[1,])){
    output[i] <- rgb(red = col.rgb[1,i],green = col.rgb[2,i],blue = col.rgb[3,i], maxColorValue = 255,alpha = alpha*255)
  }
  names(output) <- names(colours)
  return(output)
}
```

# Introduction

This is my awesome introduction that clearly defines the context and the gaps I am going to address with this beautiful paper. I will also states the hypotheses that I will test. It is going to be great, yeah yeah.

This introduction is going good, yes indeed, it will. And as it has been proven before [@harrison_back_2019; @ho_climate_2019], this has not been proven before. Evennnn better!

  \newpage

# Methods

So I used a very cool method [@ho_climate_2019]. Yeah yeah, but see also [@harrison_back_2019]. Oh and there is also [@salih_fluorescent_2000], or [@baird_effects_2018].

Here is the model I used (it is an awesome model):

\begin{align}
\frac{\mathrm{d} n}{\mathrm{d} t} = \underbrace{c n \left(1 - \frac{n}{N}\right)}_{\textrm{birth}} - \underbrace{e n}_{\textrm{death}}, \label{levins}
\end{align}

  \newpage

# Results


We can see that the variables increase and plato to a maximum value (Figure \ref{fig:figure1}). But my favorite figure is Figure \ref{fig:myfigure}.


# Discussion

# Acknowledgements

The author acknowledges feedback and advice from the editor,
Tim Coulson and two anonymous reviewers. This work was supported in
part by  USDA National Institute of Food and Agriculture, Hatch
project CA-B-INS-0162-H.

# References


\newpage

\begin{landscape}

```{r figure1, figure1, fig.cap="\\label{fig:figure1}Population dynamics from a Gillespie simulation of the Levins model with large (N=1000, panel A) and small (N=100, panel B) number of sites (blue) show relatively weaker effects of demographic noise in the bigger system. Models are otherwise identical, with e = 0.2 and c = 1 (code in appendix A). Theoretical predictions for mean and plus/minus one standard deviation shown in horizontal re dashed lines.", out.extra='angle=0', fig.align='center', fig.width=4.5, fig.height=3}
# create colour palette
colours <- ptol_pal()(2)

# load-data
data <- read_csv(here::here("Dataset_raw/gillespie.csv"), col_types = "cdiddd")  

# recode-data
data <- data %>% 
  mutate(system_size = recode(system_size, large = "A. 1000 total sites", small= "B. 100 total sites")) 

# plot-gillespie
data %>%
  ggplot(aes(x = time)) + 
  geom_hline(aes(yintercept = mean), lty=2, col=colours[2]) + 
  geom_hline(aes(yintercept = minus_sd), lty=2, col=colours[2]) + 
  geom_hline(aes(yintercept = plus_sd), lty=2, col=colours[2]) + 
  geom_line(aes(y = n), col=colours[1]) +
  facet_wrap(~system_size, scales = "free_y")
```

```{r myfigure, fig.cap="\\label{fig:myfigure}The is my figure. It is awesome. Plus it does not use ggplot, which is even better. It shows the level of happiness relatively to the amount of cheese people eat.", fig.width=4.5, fig.height=3}
colPts <- add.transparency.colour(colours = "grey60", alpha = 0.35)

df <- data.frame()
group.var <- c("never","once a month","every day")
for(i in 1:length(group.var)){
  happynesshere <- rnorm(n = 100, mean = 0, sd = 2) + i*3
  df.parthere <- cbind(rep(group.var[i],length(happynesshere)),happynesshere)
  df <- rbind(df,df.parthere)
}
names(df) <- c("Cheese_freq","happiness")
df$happiness <- as.numeric(as.character(df$happiness))
par(mar=c(4,4,0.5,0.5))
stripchart(x = happiness ~ Cheese_freq, data = df, vertical = T, method = "jitter", pch = 16, col =  colPts, cex = 1.5, las = 1)
par(new = T)
colHere <- add.transparency.colour(colours = "white", alpha = 0)
boxplot(happiness ~ Cheese_freq, data = df, horizontal = F, col = colHere, at =  1:length(levels(df$Cheese_freq)), add = T, outline = F, names = c("","",""), xaxt="n", yaxt = "n", boxwex=0.5)
mean.here <- tapply(df$happiness, df$Cheese_freq, mean)
points(y = mean.here, x = 1:length(mean.here), cex = 2, pch = 16)
```

\end{landscape}

